A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-11-02 doc/large_strain.tex
few line breaks
switch to IJNME template

\RequirePackage[l2tabu, orthodox]{nag}
%\documentclass[12pt]{article}
\documentclass[preprint,12pt,times]{elsarticle}

\biboptions{sort&compress,comma,square}

% \usepackage{url}

% \usepackage[linesnumbered,lined,commentsnumbered,ruled]{algorithm2e}
%\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage{amsfonts}
\usepackage{bm}
%\usepackage{bbm}
%\usepackage{caption}
\usepackage{xcolor}
%\usepackage{geometry}
%\usepackage{graphicx}
%\usepackage[colorlinks,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{listings}
\lstset{ %
   backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
   basicstyle=\small,        % the size of the fonts that are used for the code
   breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
   breaklines=false,                 % sets automatic line breaking
   captionpos=b,                    % sets the caption-position to bottom
   %commentstyle=\color{mygreen},    % comment style
   deletekeywords={...},            % if you want to delete keywords from the given language
   escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
   extendedchars=false,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
   frame=single,	                   % adds a frame around the code
   keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
   keywordstyle=\color{blue},       % keyword style
   language=C++,                 % the language of the code
   otherkeywords={*,...},           % if you want to add more keywords to the set
   numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
   numbersep=5pt,                   % how far the line-numbers are from the code
   numberstyle=\tiny\color{gray}, % the style that is used for the line-numbers
   rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
   showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
   showstringspaces=false,          % underline spaces within strings only
   showtabs=false,                  % show tabs within strings adding particular underscores
   stepnumber=2,                    % the step between two line-numbers. If it is 1, each line will be numbered
%   stringstyle=\color{mymauve},     % string literal style
   tabsize=2,	                   % sets default tabsize to 2 spaces
   title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}
%\usepackage{layouts}
%\usepackage{mathrsfs}
%\usepackage{pgfkeys,pgfmath,pgfcore}
%\usepackage{srcltx}
%\usepackage[labelformat=simple]{subcaption}
%\usepackage{xspace}
\usepackage[linesnumbered,lined,commentsnumbered,ruled]{algorithm2e}

@@

%\renewcommand{\thetable}{\arabic{table}}
%\captionsetup[table]{labelformat=simple, labelsep=colon}

%\pgfkeys{/pgf/number format/.cd,1000 sep={}}

%% see http://tex.stackexchange.com/questions/2441/how-to-add-a-forced-line-break-inside-a-table-cell
%\newcommand{\specialcell}[2][c]{%
%  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

% put your own definitions here:
% \renewcommand\thesubfigure{(\alph{subfigure})}
\def\gz  #1{           \mbox{$\boldsymbol{#1}$}}
% \DeclareMathAlphabet{\bsf}{OT1}{cmss}{bx}{n}
% \def\msf  #1{           \mbox{\!\!      $\sf #1$}}
\def\Grad #1 {{\rm Grad} #1}
\def\grad {\mbox{grad}}
\def\Div {\mbox{Div\,}}
\def\div {\mbox{div\,}}
\def\d {\mbox{d}}
\def\D {\mbox{D}}
% \newcommand{\norm}[1]{\left\lvert #1 \right\rvert}
%\newcommand\normDouble[1]{\left\lVert#1\right\rVert}
%\newcommand{\normXY}[1]{\lvert #1 \rvert_{2d}}
%\newcommand{\dbracket}[1]{\left[\!\!\left[ #1 \right]\!\!\right]}

\def\mcl  #1{               {\cal #1}}
%\def\bcl  #1{\mbox{\boldmath$\cal #1$}}

%\DeclareMathOperator{\det}{det}
\DeclareMathOperator{\trace}{tr}
\newcommand{\diff}{\mathop{}\!\mathrm{d}}

@@

\begin{frontmatter}
  \title{
  A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid
  }

  \author[a]{Denis Davydov\corref{cor}}
  \ead{denis.davydov@fau.de}

  \author[a]{Jean-Paul Pelteret}
  \ead{jean-paul.pelteret@fau.de}

  \author[b]{Daniel Arndt}
  \ead{daniel.arndt@iwr.uni-heidelberg.de}

  \author[a,c]{Paul Steinmann}
  \ead{paul.steinmann@fau.de}

  \cortext[cor]{Corresponding author.}

  \address[a]{Chair of Applied Mechanics,
  Friedrich-Alexander-Universit\"{a}t Erlangen-N\"{u}rnberg,
  Egerlandstr.\ 5, 91058 Erlangen, Germany}

  \address[b]{Interdisciplinary Center for Scientific Computing (IWR),
      Heidelberg University,
      Im Neuenheimer Feld 205,
      69120 Heidelberg,
      Germany}

  \address[c]{Glasgow Computational Engineering Center (GCEC),
      University of Glasgow, G12 8QQ Glasgow, United Kingdom
  }

@@

  \begin{keyword}
      adaptive finite element method \sep
      geometric multigrid \sep
      finite-strain \sep
      matrix-free \sep
      hyperelasticity
  \end{keyword}

  \end{frontmatter}

>>>>

\RequirePackage[l2tabu, orthodox]{nag}
%\documentclass[12pt]{article}
% \documentclass[preprint,12pt,times]{elsarticle}
\documentclass[times,doublespace]{nmeauth}

%%% ELSOPTIONS:
% \biboptions{sort&compress,comma,square}
% \usepackage{amsmath}

%%%

\usepackage{bm}
\usepackage{xcolor}
\usepackage{listings}
\lstset{ %
   backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
   basicstyle=\small,        % the size of the fonts that are used for the code
   breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
   breaklines=false,                 % sets automatic line breaking
   captionpos=b,                    % sets the caption-position to bottom
   %commentstyle=\color{mygreen},    % comment style
   deletekeywords={...},            % if you want to delete keywords from the given language
   escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
   extendedchars=false,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
   frame=single,	                   % adds a frame around the code
   keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
   keywordstyle=\color{blue},       % keyword style
   language=C++,                 % the language of the code
   otherkeywords={*,...},           % if you want to add more keywords to the set
   numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
   numbersep=5pt,                   % how far the line-numbers are from the code
   numberstyle=\tiny\color{gray}, % the style that is used for the line-numbers
   rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
   showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
   showstringspaces=false,          % underline spaces within strings only
   showtabs=false,                  % show tabs within strings adding particular underscores
   stepnumber=2,                    % the step between two line-numbers. If it is 1, each line will be numbered
%   stringstyle=\color{mymauve},     % string literal style
   tabsize=2,	                   % sets default tabsize to 2 spaces
   title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}
\usepackage[linesnumbered,lined,commentsnumbered,ruled]{algorithm2e}

@@

%
% Definitions:
%
\def\gz  #1{           \mbox{$\boldsymbol{#1}$}}
\def\Grad #1 {{\rm Grad} #1}
\def\grad {\mbox{grad}}
\def\Div {\mbox{Div\,}}
\def\div {\mbox{div\,}}
\def\d {\mbox{d}}
\def\D {\mbox{D}}
\def\mcl  #1{               {\cal #1}}
\DeclareMathOperator{\trace}{tr}
\newcommand{\diff}{\mathop{}\!\mathrm{d}}

@@

\runningheads{D. Davydov et al.}{A matrix-free approach for finite-strain hyperelastic problems}

\title{
  A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid
  }

  \author{
    Denis Davydov\affil{1} \corrauth ,
    Jean-Paul Pelteret\affil{1},
    Daniel Arndt\affil{2},
    Paul Steinmann\affil{1,3}
  }

  \address{
    \affilnum{1}Chair of Applied Mechanics,
    Friedrich-Alexander-Universit\"{a}t Erlangen-N\"{u}rnberg,
    Egerlandstr.\ 5, 91058 Erlangen, Germany \break
    \affilnum{2}Interdisciplinary Center for Scientific Computing (IWR),
    Heidelberg University,
    Im Neuenheimer Feld 205, 69120 Heidelberg, Germany \break
    \affilnum{3}Glasgow Computational Engineering Center (GCEC),
        University of Glasgow, G12 8QQ Glasgow, United Kingdom \break
    }

  \corraddr{E-mail: denis.davydov@fau.de}

  % \author[a]{Denis Davydov\corref{cor}}
  % \ead{denis.davydov@fau.de}

  % \author[a]{Jean-Paul Pelteret}
  % \ead{jean-paul.pelteret@fau.de}

  % \author[b]{Daniel Arndt}
  % \ead{daniel.arndt@iwr.uni-heidelberg.de}

  % \author[a,c]{Paul Steinmann}
  % \ead{paul.steinmann@fau.de}

  % \cortext[cor]{Corresponding author.}

  % \address[a]{Chair of Applied Mechanics,
  % Friedrich-Alexander-Universit\"{a}t Erlangen-N\"{u}rnberg,
  % Egerlandstr.\ 5, 91058 Erlangen, Germany}

  % \address[b]{Interdisciplinary Center for Scientific Computing (IWR),
  %     Heidelberg University,
  %     Im Neuenheimer Feld 205,
  %     69120 Heidelberg,
  %     Germany}

  % \address[c]{Glasgow Computational Engineering Center (GCEC),
  %     University of Glasgow, G12 8QQ Glasgow, United Kingdom
  % }

@@

  \keywords{
  % \begin{keyword}
      adaptive finite element method ; %\sep
      geometric multigrid ; %\sep
      finite-strain ; %\sep
      matrix-free ; %\sep
      hyperelasticity
  % \end{keyword}
  }

  \maketitle
  % \end{frontmatter}
